A planetary collision afterglow and transit of the resultant debris cloud

### 2023-10-12 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
\begin{centering}
\includegraphics[width=\textwidth]{figures/all_phot_nature_delta_flux.pdf}
\caption{\textbf{Optical and infrared photometry of ASASSN-21qj.}
%
{\bf a}, Normalized optical photometry from \gls{asassn} in the $V$-band and the $g'$ band.
%
{\bf b},Fractional flux increase in brightness of ASASSN-21qj in both the $W1$ and $W2$ bands, for which a value of 1.0 represents the stellar contribution alone.
%
{\bf c},Calculated NEOWISE color temperature estimated from the photometry of the two bands.
%
The color temperature is plotted as zero when there is no infrared excess and is consistent with a temperature of 1000\,K while the excess is present.
%
Error bars are shown at $1\sigma$ confidence.
}
\label{fig:wisephot}
\script{plot_all_phot_nature_delta_flux.py}
\end{centering}
\end{figure}

@@

\begin{figure}[h!]
    \centering
\includegraphics[width=0.8\textwidth]{figures/sed.pdf}
    \caption{\textbf{Spectrum of \asas{}~components.}
    %
    The red symbols show the optical and pre-brightnening \gls{wise} infrared photometry and the blue symbols show the post-brightnening \gls{wise} and \gls{alma} fluxes.
    %
    Stellar and 1000\,K components consistent with the pre- and post-brightening fluxes are shown.
    %
    The dashed line shows an estimated cool component spectrum for \SI{0.1}{\micro\metre}-sized grains associated with the transiting dust cloud.
    %
    Downward triangles are upper limits.
    %
    Error bars are shown at $1\sigma$ confidence.
}
    \label{fig:sed}
   \script{fvsr.py}
\end{figure}
%

@@

\begin{figure}
   \begin{centering}
\includegraphics[width=\textwidth]{figures/tess_asas_ls_epochs.pdf}
      \caption{\textbf{The light curve of ASASSN-21qj from \gls{tess} and the periodogram of \gls{tess} and \gls{asassn} photometry.}
      %
      {\bf a,b},Photometry of ASASSN-21qj from three sectors of \gls{tess}.
      %
      {\bf c},Lomb-Scargle analysis of photometry from \gls{tess} (colored blue) and from \gls{asassn} V band data from MJD 57420 to MJD 58386 (light grey) shows a signal at 4.4 days.
      %
      At lower frequencies, the ground based photometry shows power and aliasing signals.
      %
      The \gls{tess} signal shows a significant signal at 4.43 days, and a similar signal is seen in the ground-based data.
      %
      The longer time baseline in the \gls{asassn} data reveals substructure in the signal.}
        \label{fig:TESS_lc}
        \script{plot_tess_asas_ls_epochs.py}
    \end{centering}
\end{figure}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=1.0\textwidth]{figures/master_lightcurve_nature_with_zoom_3_panel.pdf}
      \caption{\textbf{Deriving the transverse velocity from a light curve.}
      %
      {\bf a},\gls{asassn} $g'$ photometry is shown in units of normalised flux.
      %
      Straight line fits (light-blue lines) are made to the photometry in the regions indicated by the light-grey vertical lines.
      %
      {\bf b},Gradient of the light curve as a function of time.
      %
      {\bf c},Transverse velocity derived from the light curve and the gradient of the light curve.
      %
      Error bars are shown at $1\sigma$ confidence.
}
        \label{fig:gradientconvert}
\script{plot_master_lightcurve_nature_with_zoom_3_panel.py}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=\textwidth]{figures/all_phot_nature_delta_flux.pdf}
\caption{\textbf{Optical and infrared photometry of ASASSN-21qj.}
%
{\bf a}, Normalized optical photometry from ASAS-SN in the $V$-band and the $g'$ band.
%
{\bf b},Fractional flux increase in brightness of ASASSN-21qj in both the $W1$ and $W2$ bands, for which a value of 1.0 represents the stellar contribution alone.
%
{\bf c},Calculated NEOWISE color temperature estimated from the photometry of the two bands.
%
The color temperature is plotted as zero when there is no infrared excess and is consistent with a temperature of 1000\,K while the excess is present.
%
Error bars are shown at $1\sigma$ confidence.
}
\label{fig:wisephot}
\script{plot_all_phot_nature_delta_flux.py}
\end{centering}
\end{figure}

@@

\begin{figure}[h!]
    \centering
\includegraphics[width=0.8\textwidth]{figures/sed.pdf}
    \caption{\textbf{Spectrum of \asas{}~components.}
    %
    The red symbols show the optical and pre-brightnening WISE infrared photometry and the blue symbols show the post-brightnening WISE and ALMA fluxes.
    %
    Stellar and 1000\,K components consistent with the pre- and post-brightening fluxes are shown.
    %
    The dashed line shows an estimated cool component spectrum for $0.1\mu m$\SI{0.1}{\micro\metre}-sized grains associated with the transiting dust cloud.
    %
    Downward triangles are upper limits.
    %
    Error bars are shown at $1\sigma$ confidence.
}
    \label{fig:sed}
   \script{fvsr.py}
\end{figure}
%

@@

\begin{figure}
   \begin{centering}
\includegraphics[width=\textwidth]{figures/tess_asas_ls_epochs.pdf}
      \caption{\textbf{The light curve of ASASSN-21qj from TESS and the periodogram of TESS and ASAS-SN photometry.}
      %
      {\bf a,b},Photometry of ASASSN-21qj from three sectors of TESS.
      %
      {\bf c},Lomb-Scargle analysis of photometry from TESS (colored blue) and from ASAS-SN V band data from MJD 57420 to MJD 58386 (light grey) shows a signal at 4.4 days.
      %
      At lower frequencies, the ground based photometry shows power and aliasing signals.
      %
      The TESS signal shows a significant signal at 4.43 days, and a similar signal is seen in the ground-based data.
      %
      The longer time baseline in the ASAS-SN data reveals substructure in the signal.}
        \label{fig:TESS_lc}
        \script{plot_tess_asas_ls_epochs.py}
    \end{centering}
\end{figure}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=1.0\textwidth]{figures/master_lightcurve_nature_with_zoom_3_panel.pdf}
      \caption{\textbf{Deriving the transverse velocity from a light curve.}
      %
      {\bf a},ASAS-SN $g'$ photometry is shown in units of normalised flux.
      %
      Straight line fits (light-blue lines) are made to the photometry in the regions indicated by the light-grey vertical lines.
      %
      {\bf b},Gradient of the light curve as a function of time.
      %
      {\bf c},Transverse velocity derived from the light curve and the gradient of the light curve.
      %
      Error bars are shown at $1\sigma$ confidence.
}
        \label{fig:gradientconvert}
\script{plot_master_lightcurve_nature_with_zoom_3_panel.py}
